\bf \texttt{forestecology} package for modeling interspecies competition between trees

### 2021-01-08 etc/paper/forestecology.Rmd
Setup MEE formatting

authors: 
- name: Albert Y. Kim 
  thanks: "Albert Y. Kim is Assistant Professor, Statistical & Data Sciences, Smith College, Northampton, MA 01063 (e-mail: akim04@smith.edu). This work was not supported by any grant. The authors thank numerous colleagues and students for their support."
  affiliation: Program in Statistical & Data Sciences, Smith College

@@

keywords:
- forestecology, trees

abstract: 
- "We provide a computational exercise suitable for early introduction in an undergraduate statistics or data science course that allows students to 'play the whole game' of data science: performing both data collection and data analysis. While many teaching resources exist for data analysis, such resources are not as abundant for data collection given the inherent difficulty of the task. Our proposed exercise centers around student use of Google Calendar to collect data with the goal of answering the question 'How do I spend my time?' On the one hand, the exercise involves answering a question with near universal appeal, but on the other hand, the data collection mechanism is not beyond the reach of a typical undergraduate student. A further benefit of the exercise is that it provides an opportunity for discussions on ethical questions and considerations that data providers and data analysts face in today's age of large-scale internet-based data collection."

bibliography: paper.bib
output: rticles::asa_article
link-citations: yes
header-includes:
- \usepackage{xcolor, soul, xspace, float, subfig}
---

@@

@@

# Conclusions

>>>>

authors: 
- name: Albert Y. Kim 
  thanks: "Albert Y. Kim is Assistant Professor, Statistical & Data Sciences, Smith College, Northampton, MA 01063 (e-mail: akim04@smith.edu)."
  affiliation: Program in Statistical & Data Sciences, Smith College

@@

abstract: 
- "Move abstract below here after completed."

keywords:
- forest ecology, competition, R, Rstats, tidyverse, sf, cross-validation,

bibliography: paper.bib
output: rticles::asa_article
link-citations: yes
header-includes:
- \usepackage{xcolor, soul, xspace, float, subfig, lineno}
---

\linenumbers

@@

# Abstract (350 words)

1. set the context for and purpose of the work 
1. indicate the approach and the methods 
1. outline the main results 
1. identify the conclusions and wider implications

@@

# Discussion

### 2021-01-08 etc/paper/forestecology.tex
Setup MEE formatting

\usepackage{xcolor, soul, xspace, float, subfig}

@@

  \author{
        Albert Y. Kim \thanks{Albert Y. Kim is Assistant Professor, Statistical \& Data Sciences,
Smith College, Northampton, MA 01063 (e-mail:
\href{mailto:akim04@smith.edu}{\nolinkurl{akim04@smith.edu}}). This work
was not supported by any grant. The authors thank numerous colleagues
and students for their support.} \\
    Program in Statistical \& Data Sciences, Smith College\\
     and \\     David Allen \\
    Biology Department, Middlebury College\\
      }
  \maketitle
} \fi

@@

\bigskip
\begin{abstract}
We provide a computational exercise suitable for early introduction in
an undergraduate statistics or data science course that allows students
to `play the whole game' of data science: performing both data
collection and data analysis. While many teaching resources exist for
data analysis, such resources are not as abundant for data collection
given the inherent difficulty of the task. Our proposed exercise centers
around student use of Google Calendar to collect data with the goal of
answering the question `How do I spend my time?' On the one hand, the
exercise involves answering a question with near universal appeal, but
on the other hand, the data collection mechanism is not beyond the reach
of a typical undergraduate student. A further benefit of the exercise is
that it provides an opportunity for discussions on ethical questions and
considerations that data providers and data analysts face in today's age
of large-scale internet-based data collection.
\end{abstract}

\noindent%
{\it Keywords:} forestecology, trees
\vfill

@@

@@

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

>>>>

\usepackage{xcolor, soul, xspace, float, subfig, lineno}

@@

  \author{
        Albert Y. Kim \thanks{Albert Y. Kim is Assistant Professor, Statistical \& Data Sciences,
Smith College, Northampton, MA 01063 (e-mail:
\href{mailto:akim04@smith.edu}{\nolinkurl{akim04@smith.edu}}).} \\
    Program in Statistical \& Data Sciences, Smith College\\
     and \\     David Allen \\
    Biology Department, Middlebury College\\
      }
  \maketitle
} \fi

@@

\bigskip
\begin{abstract}
Move abstract below here after completed.
\end{abstract}

\noindent%
{\it Keywords:} forest ecology, competition, R, Rstats, tidyverse, sf, cross-validation,
\vfill

@@

\linenumbers

\hypertarget{abstract-350-words}{%
\section{Abstract (350 words)}\label{abstract-350-words}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  set the context for and purpose of the work
\item
  indicate the approach and the methods
\item
  outline the main results
\item
  identify the conclusions and wider implications
\end{enumerate}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}
